Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-23 tsibbletalk.Rmd
overview of interactivity

The R community has a long-standing contribution to interactive visualisation systems in abundance. These systems can be roughly divided into two classes: ones with web technology and the others without.

R \CRANpkg{shiny} [@R-shiny] and \CRANpkg{htmlwidgets} [@R-htmlwidgets] lay a fundamental infrastructure in marrying R with HTML elements and JavaScript for interactivity, although they seldom emphasise on interactive graphics. The \CRANpkg{htmlwidgets} package opens a door to embedding JavaScript libraries into R such that users are able to write only R code to generate web-based plots. Many JavaScript charting libraries have been ported to R as HTML widgets, including \CRANpkg{plotly} [@plotly2020], \CRANpkg{rbokeh} [@R-rbokeh], and \CRANpkg{leaflet} [@R-leaflet] for maps. To enable interactions between different widgets, it can be achieved with \CRANpkg{shiny} or \CRANpkg{crosstalk} [@R-crosstalk]. The \CRANpkg{crosstalk} extends \CRANpkg{htmlwidgets} with shared R6 instances to support linked brushing and filtering across widgets, without relying on \CRANpkg{shiny}.

If not using web technology, two examples are provided here: \CRANpkg{loon} [@R-loon] based on Tcl/Tk and \pkg{cranvas} [@xie_reactive_2014] based on Qt. They offer a wide array of pre-defined interactions, such as selecting and zooming, to manipulate plots via mouse, keyboard strokes, and menus. The \pkg{cranvastime} package [@cheng_enabling_2016] is an add-on of \pkg{cranvas}, which develops a set of novel interactions for temporal data, for example wrapping and mirroring.

>>>>

There is a long history of interactive data visualisation research and corresponding systems. Within R, the systems can be roughly divided into systems utilising web technology and those that don't.

R \CRANpkg{shiny} [@R-shiny] and \CRANpkg{htmlwidgets} [@R-htmlwidgets] provides and infrastructure connecting R with HTML elements and JavaScript that provide the interactivity.<!--, although they seldom emphasise on interactive graphics.--> The \CRANpkg{htmlwidgets} package makes it possible to embed JavaScript libraries into R so that users are able to write only R code to generate web-based plots. Many JavaScript charting libraries have been ported to R as HTML widgets, including \CRANpkg{plotly} [@plotly2020], \CRANpkg{rbokeh} [@R-rbokeh], and \CRANpkg{leaflet} [@R-leaflet] for maps. Interactions between different widgets can be achieved with \CRANpkg{shiny} or \CRANpkg{crosstalk} [@R-crosstalk]. The \CRANpkg{crosstalk} extends \CRANpkg{htmlwidgets} with shared R6 instances to support linked brushing and filtering across widgets, without relying on \CRANpkg{shiny}.

Systems without the web technology include \CRANpkg{loon} [@R-loon], based on Tcl/Tk, and \pkg{cranvas} [@xie_reactive_2014] based on Qt. They offer a wide array of pre-defined interactions, such as selecting and zooming, to manipulate plots via mouse action, keyboard strokes, and menus. The \pkg{cranvastime} package [@cheng_enabling_2016] is an add-on to \pkg{cranvas}, which provides specialised interactions for temporal data, such as wrapping and mirroring.

### 2020-09-23 tsibbletalk.tex
overview of interactivity

The R community has a long-standing contribution to interactive
visualisation systems in abundance. These systems can be roughly divided
into two classes: ones with web technology and the others without.

R \CRANpkg{shiny} \citep{R-shiny} and \CRANpkg{htmlwidgets}
\citep{R-htmlwidgets} lay a fundamental infrastructure in marrying R
with HTML elements and JavaScript for interactivity, although they
seldom emphasise on interactive graphics. The \CRANpkg{htmlwidgets}
package opens a door to embedding JavaScript libraries into R such that
users are able to write only R code to generate web-based plots. Many
JavaScript charting libraries have been ported to R as HTML widgets,
including \CRANpkg{plotly} \citep{plotly2020}, \CRANpkg{rbokeh}
\citep{R-rbokeh}, and \CRANpkg{leaflet} \citep{R-leaflet} for maps. To
enable interactions between different widgets, it can be achieved with
\CRANpkg{shiny} or \CRANpkg{crosstalk} \citep{R-crosstalk}. The
\CRANpkg{crosstalk} extends \CRANpkg{htmlwidgets} with shared R6
instances to support linked brushing and filtering across widgets,
without relying on \CRANpkg{shiny}.

If not using web technology, two examples are provided here:
\CRANpkg{loon} \citep{R-loon} based on Tcl/Tk and \pkg{cranvas}
\citep{xie_reactive_2014} based on Qt. They offer a wide array of
pre-defined interactions, such as selecting and zooming, to manipulate
plots via mouse, keyboard strokes, and menus. The \pkg{cranvastime}
package \citep{cheng_enabling_2016} is an add-on of \pkg{cranvas}, which
develops a set of novel interactions for temporal data, for example
wrapping and mirroring.

>>>>

There is a long history of interactive data visualisation research and
corresponding systems. Within R, the systems can be roughly divided into
systems utilising web technology and those that don't.

R \CRANpkg{shiny} \citep{R-shiny} and \CRANpkg{htmlwidgets}
\citep{R-htmlwidgets} provides and infrastructure connecting R with HTML
elements and JavaScript that provide the interactivity. The
\CRANpkg{htmlwidgets} package makes it possible to embed JavaScript
libraries into R so that users are able to write only R code to generate
web-based plots. Many JavaScript charting libraries have been ported to
R as HTML widgets, including \CRANpkg{plotly} \citep{plotly2020},
\CRANpkg{rbokeh} \citep{R-rbokeh}, and \CRANpkg{leaflet}
\citep{R-leaflet} for maps. Interactions between different widgets can
be achieved with \CRANpkg{shiny} or \CRANpkg{crosstalk}
\citep{R-crosstalk}. The \CRANpkg{crosstalk} extends
\CRANpkg{htmlwidgets} with shared R6 instances to support linked
brushing and filtering across widgets, without relying on
\CRANpkg{shiny}.

Systems without the web technology include \CRANpkg{loon}
\citep{R-loon}, based on Tcl/Tk, and \pkg{cranvas}
\citep{xie_reactive_2014} based on Qt. They offer a wide array of
pre-defined interactions, such as selecting and zooming, to manipulate
plots via mouse action, keyboard strokes, and menus. The
\pkg{cranvastime} package \citep{cheng_enabling_2016} is an add-on to
\pkg{cranvas}, which provides specialised interactions for temporal
data, such as wrapping and mirroring.
